Universals of word order result from optimization of grammars for efficient communication

### 2019-03-25 second-draft/3-paper-names.tex
revising

These are shown in Table~\ref{table:corr-dryer}.
We compare the prevalence of the word order correlations in optimized languages (right) to their prevalence in the real languages (left).
%To evaluate their presence in real languages, we tested for the correlations in word order grammars fit by maximum likelihood to actual orderings from treebanks.
%The word order correlations detected this way match linguistic descriptions compiled in the World Atlas of Linguistic Structures (WALS, \cite{wals}) to the extent that they are documented in WALS. %in all except four languages, for WALS did not have data.
Table~\ref{table:corr-dryer} shows that grammars optimized for efficiency accurately predict correlations to hold at prevalences similar to actual languages.

In Figure~\ref{fig:per-lang}, we show results on the levels of individual languages.
For every one of the 51 languages, we show orders predicted by efficiency, for the eight correlating pairs.
For each language, we construct a grammar optimized for efficiency with the direction of the verb-object relation fixed to correspond to the actual language.

>>>>

We compare grammars optimized for efficiency with the actual grammars of the 51 languages, as extracted from the orderings attested in the original corpora (see \textit{Materials and Methods}).

The eight correlations are shown in Table~\ref{table:corr-dryer}.
We compare the prevalence of the word order correlations in optimized languages (right) to their prevalence in the real languages (left).
%To evaluate their presence in real languages, we tested for the correlations in word order grammars fit by maximum likelihood to actual orderings from treebanks.
%The word order correlations detected this way match linguistic descriptions compiled in the World Atlas of Linguistic Structures (WALS, \cite{wals}) to the extent that they are documented in WALS. %in all except four languages, for WALS did not have data.
Table~\ref{table:corr-dryer} shows that grammars optimized for efficiency accurately predict correlations to hold at prevalences similar to actual languages.

In Figure~\ref{fig:per-lang}, we show results on the levels of individual languages.
For every one of the 51 languages, we show orders predicted by efficiency, for the eight correlating pairs.
For each language, we construct a grammar optimized for efficiency with the direction of the verb-object relation fixed to correspond to the actual language.
Predictions of efficiency optimization broadly agree with the actual word order patterns.
%Note that perfect agreement is not to be expected, as grammars will be impacted by factors such as historical development.
%For instance, Dutch (nld) and Afrikaans (afr) have a prevalence of object-verb order, and
